### 2023-01-04 _posts/papers-2023.tex
Add ARM Neoverse citation

\begin{itemize}
    \item Ericsson's experience with virtual platform for pre-silicon software development. The virtual platforms are based on SystemC/TLM. This paper may be used as a showcase of simulation importance.

@@

>>>>

\begin{itemize}
    \item Ericsson's experience with virtual platform for pre-silicon software development. The virtual platforms are based on SystemC/TLM. This paper may be used as a showcase of simulation importance:

@@

\section*{Processors}
\begin{itemize}
    \item A 64 core ARM reference server CPU design similar to Cortex-A76 microarchitecture. Single core performance is not that good but the processor is expectedly much more power efficient. New hardware-based coherence model for i-cache aiming improvement for multiple VM performance. SPEC CPU 2006 is still referenced as a benchmark. Interesting reference to read --- <<Editorial: Intel Hides Behind ICC>> --- MPR claims that ICC must be approximately 30\% faster than GCC (at least for SPEC workloads):

    \cite{Gwennap:ARM-Neoverse:2019}.
\end{itemize}
